Weed and Corn segmentation through Convolutional Neuronal Networks

### 2017-06-02 PaperBCJ.tex
Fix Training Graph

\subsection{Dataset Description}
Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the  the Ecuadoring Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose. \\

Samples were obtained from images captured in those maize fields , we considered to choose Maize Crops where we could visually discriminate the plants of the crop and the weed.  To record the samples we centered the camera insuring that the capture shows all the features of the maize plant, it was possible by monitoring the get of samples by an external display. An examples of the images captured are shown below. 
\\

@@

	\begin{figure}[h]
	\centering
	\includegraphics[width=3.5in]{entrenamiento}
	\caption{ Left: Accuracy vs Iterations, Right: Loss vs Iterations}
	\label{fig_sim}
	\end{figure}

@@

>>>>

\subsection{Dataset Description}
Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the  the Ecuadorian Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose. \\

Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed. Maize in stages V3-V7(3-7 leafs) \cite{Fassio} were used to take samples. To record the samples we centered the camera insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display. An examples of the images captured are shown below. 
\\

@@

	\begin{figure}[h]
	\centering
	\includegraphics[width=3.2in]{entrenamiento}
	\caption{ Graph of the Training Process }
	\label{fig_sim}
	\end{figure}

@@

       \bibitem{Fassio}
Fassio, A., Carriquiry, A., Tojo, C. and Romero, R  \emph{MAIZ: Aspectos sobre fenolog\'ia}  \hskip 1em plus
  0.5em minus 0.4em\relax Montevideo, Uruguay:Seria T\'ecnica Nº 101, 1998.
